Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-09-05 paper/pool_model.tex
replace old abm figures

        {Figures/abm-homogenous/snapshot_00006000.png}

@@

        {Figures/abm-homogenous/snapshot_00012000.png}

@@

        {Figures/abm-homogenous/snapshot_00018000.png}

@@

        {Figures/abm-homogenous/snapshot_00024000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous-low-diffusion/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous/snapshot_00012000.png}%

@@

        \includegraphics[width=\textwidth]{Figures/abm-random/snapshot_00012000.png}%

>>>>

        {Figures/abm-homogenous/images/snapshot_00006000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00012000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00018000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00024000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous/images/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous-low-diffusion/images/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous/images/snapshot_00012000.png}%

@@

        \includegraphics[width=\textwidth]{Figures/abm-random/images/snapshot_00012000.png}%
